Prediction of 90-day mortality after Total Hip Arthroplasty: a simplified and externally validated model based on observational registry data from Sweden, England and Wales

### 2020-09-09 reports/article.Rmd
fixed wrong fig ref.

The main and reduced models were no different regarding discriminative ability `r sprintf("%s versus %s", gsub(")", "", get_auc("Main model"), fixed = TRUE), gsub("(", "", get_auc("Reduced model"), fixed = TRUE))`. We therefore considered the reduced model as superior due to its simplicity. Traditional models performed poorly with 95&nbsp;% confidence intervals not above 0.7: The Charlson comorbidity index had an AUC of `r half_paran("Charlson")` and the Elixhauser comorbidity an AUC of `r gsub("\\)", ";", half_paran("Elixhauser"))` Figure \@ref(fig:rocvalidation) and Figure \@ref(fig:aucci)).

@@

We found that a multivariable main effects logistic regression model with `r coefs_print_reduced` was better at predicting death within 90 days after THA than traditional models based on the Charlson or Elixhauser comorbidity indices. The resulting model predicted the probability of death within 90 days as: $\hat p = 1 / [1 +\exp(-\hat \beta x)]$ where $\hat \beta$ is the vector of estimated coefficients (including intercept) presented in table \@ref(tab:brlreduced).
This formula is considered valid for patients aged ~~`r age_range`~~ years and for predicted probabilities up to 5&nbsp;%.

>>>>

The main and reduced models were no different regarding discriminative ability `r sprintf("%s versus %s", gsub(")", "", get_auc("Main model"), fixed = TRUE), gsub("(", "", get_auc("Reduced model"), fixed = TRUE))`. We therefore considered the reduced model as superior due to its simplicity. Traditional models performed poorly with 95&nbsp;% confidence intervals not above 0.7: The Charlson comorbidity index had an AUC of `r half_paran("Charlson")` and the Elixhauser comorbidity an AUC of `r gsub("\\)", ";", half_paran("Elixhauser"))` Figure \@ref(fig:rocderivation) and Figure \@ref(fig:aucci)).

@@

We found that a multivariable main effects logistic regression model with `r coefs_print_reduced` was better at predicting death within 90 days after THA than traditional models based on the Charlson or Elixhauser comorbidity indices. The resulting model predicted the probability of death within 90 days as: $\hat p = 1 / [1 +\exp(-\hat \beta' x)]$ where $\hat \beta$ is the vector of estimated coefficients (including intercept) presented in table \@ref(tab:brlreduced).
This formula is considered valid for patients aged ~~`r age_range`~~ years and for predicted probabilities up to 5&nbsp;%.
